%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[breaklinks=true]{hyperref}

\setlength{\textwidth}{5in} % Text width of the document
\pagestyle{plain}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Kai Li, PhD} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{\href{mailto:kli16@utk.edu}{kli16@utk.edu}}
\moveleft.5\hoffset\centerline{ORCID: \href{https://orcid.org/0000-0002-7264-365X}{\nolinkurl{0000-0002-7264-365X}} }

%----------------------------------------------------------------------------------------

\begin{resume}


\section{RESEARCH INTERESTS}  

Scholarly communication; Quantitative science studies; Digital humanities; Information organization; Science and technology studies; Information visualization

\section{ACADEMIC POSITION}

{\sl Assistant Professor} \hfill 2023 -  \\
School of Information Sciences\\
\textbf{University of Tennessee, Knoxville}, Tennessee, USA

{\sl Assistant Professor} \hfill 2020 - 2022 \\
School of Information Resource Management\\
\textbf{Renmin University of China}, Beijing, China

\section{EDUCATION}

{\sl Ph.D. in Information Studies} \hfill 2015 - 2020 \\
College of Computing \& Informatics\\
\textbf{Drexel University}, Philadelphia, PA
\begin{itemize}
\item Dissertation: A quantitative examination of research methods and software in scientific publications
\item Advisor: Dr. Erjia Yan
\end{itemize} 

{\sl Master of Science in Library and Information Science} \hfill 2012 - 2013 \\
School of Information Studies\\
\textbf{Syracuse University}, Syracuse, NY
 
{\sl Bachelor’s Degree in History} \hfill 2003 - 2007\\
School of History\\
\textbf{Beijing Normal University}, Beijing, China

% Publications section
\section{PUBLICATIONS}

\textbf{Peer-Reviewed Journal Articles}

[J21] Jiao, C., \underline{Li, K.}, \& Fang, Z. (2022). Data sharing practices across knowledge domains: a dynamic examination of data availability statements in PLOS ONE publications \textit{Journal of Information Science}, OnlineFirst. \href{https://doi.org/10.1177/0165551522110183}{\nolinkurl{https://doi.org/10.1177/0165551522110183}} 

[J20] \underline{Li, K.} (2022). Relationships between Method-section citation rates and citation contexts: Evidence from highly cited references in psychology. \textit{Online Information Review}, 46(5): 829-845 \href{https://doi.org/10.1108/OIR-03-2021-0171}{\nolinkurl{https://doi.org/10.1108/OIR-03-2021-0171}} 

[J19] Wang Y., Zhang C., \underline{Li K.} (2022) A review on method entities in the academic literature: extraction, evaluation, and application. \textit{Scientometrics}. 127: 2479-2520. \href{https://doi.org/10.1007/s11192-022-04332-7}{\nolinkurl{https://doi.org/10.1007/s11192-022-04332-7}}

[J18] Ma, R., \& \underline{Li, K.} (2022). Digital humanities as a cross-disciplinary battleground: An examination of inscriptions in journal publications. \textit{Journal of the Association for Information Science and Technology}, 73(2): 172-187. \href{https://doi.org/10.1002/asi.24534}{\nolinkurl{https://doi.org/10.1002/asi.24534}}

[J17] \underline{Li, K.} \& Jiao, C. (2022). The data paper as a socio-linguistic epistemic object: A content analysis on the rhetorical moves used in data paper abstracts. \textit{Journal of the Association for Information Science and Technology.}, 73(6): 834-846. \href{https://doi.org/10.1002/asi.24585}{\nolinkurl{https://doi.org/10.1002/asi.24585}}

[J16] \underline{Li, K.}, Jiao, C., Sugimoto, C. R., \& Lariviere, V. (2022). Versioning boundary objects: the citation profile of the Diagnostic and Statistical Manual for Mental Disorders (DSM). \textit{Journal of Documentation}, 78(4): 871-889. \href{https://doi.org/10.1108/JD-06-2021-0117}{\nolinkurl{https://doi.org/10.1108/JD-06-2021-0117}}

[J15] Lou, W. Su, Z., He, J. \& \underline{Li, K.} (2021) A temporally dynamic examination of research method usage in the Chinese library and information science community. \textit{Information Processing \& Management}, 58(5): 102686. \href{https://doi.org/10.1016/j.ipm.2021.102686}{\nolinkurl{https://doi.org/10.1016/j.ipm.2021.102686}} 

[J14] Wu C., Yan, E., Zhu, Y., \& \underline{Li, K.} (2021). Gender imbalance in the productivity of funded projects: A study of the outputs of National Institutes of Health R01 grants. \textit{Journal of the Association for Information Science and Technology}, 72(11): 1386-1399. \href{https://doi.org/10.1002/asi.24487}{\nolinkurl{https://doi.org/10.1002/asi.24487}}

[J13] \underline{Li, K.} (2021) The re-instrumentalization of the Diagnostic and Statistical Manual of Mental Disorders (DSM) in psychological publications: a citation context analysis. \textit{Quantitative Science Studies}, 2(2): 678-697. \href{https://doi.org/10.1162/qss_a_00124}{\nolinkurl{https://doi.org/10.1162/qss_a_00124}}

[J12] Lou, W., Zhang, J., \underline{Li, K.}, \& He, J. (2020). Understanding the Application of Science Mapping Tools in LIS and Non-LIS Domains. \textit{Data and Information Management}, 4(2), 94-108. \href{https://doi.org/10.2478/dim-2020-0006}{\nolinkurl{https://doi.org/10.2478/dim-2020-0006}}

[J11] Yan, E., Chen, Z. \& \underline{Li, K.} (2020). The relationship between journal citation impact and citation sentiment: A study of 32 million citances in PubMed Central, \textit{Quantitative Science Studies}, 1(2): 664-674. \href{https://doi.org/10.1162/qss\_a\_00040}{\nolinkurl{https://doi.org/10.1162/qss_a_00040}}

[J10] Yan, E., Chen, Z. \& \underline{Li, K.} (2020). Authors' status and the perceived quality of their work: Measuring citation sentiment change in nobel articles. \textit{Journal of the Association for Information Science and Technology}, 71(3): 314-324. \href{https://doi.org/10.1002/asi.24237}{\nolinkurl{https://doi.org/10.1002/asi.24237}}

[J9] \underline{Li, K.}, Greenberg, J. and Dunic, J. (2020). Data objects and documenting scientific processes: An analysis of data events in biodiversity data papers. \textit{Journal of the Association for Information Science and Technology}, 71(2): 172-182. \href{https://doi.org/10.1002/asi.24226}{\nolinkurl{https://doi.org/10.1002/asi.24226}}

[J8] \underline{Li, K.}, Chen, P.-Y., \& Yan, E. (2019). Challenges of measuring software impact through citations: An examination of the lme4 R package. \textit{Journal of Informetrics}, 13(1), 449-461. \href{https://doi.org/10.1016/j.joi.2019.02.007}{\nolinkurl{https://doi.org/10.1016/j.joi.2019.02.007}}

[J7] \underline{Li, K.}, \& Yan, E. (2019). Are NIH-funded publications fulfilling the proposed research? An examination of concept-matchedness between NIH research grants and their supported publications. \textit{Journal of Informetrics}, 13(1), 226-237. \href{https//doi.org/10.1016/j.joi.2019.01.001}{\nolinkurl{https//doi.org/10.1016/j.joi.2019.01.001}}

[J6] Li, Y., Wu, C., Yan, E., \& \underline{Li, K.} (2018). Will open access increase journal CiteScores? An empirical investigation over multiple disciplines. \textit{PLOS ONE}, 13(8): e0201885. \href{https://doi.org/10.1371/journal.pone.0201885}{\nolinkurl{https://doi.org/10.1371/journal.pone.0201885}}

[J5] Yan, E., \& \underline{Li, K.} (2018). Which domains do open-access journals do best in? A 5-year longitudinal study. \textit{Journal of the Association for Information Science and Technology}, 69(6): 844-856. \href{https://doi.org/10.1002/asi.24002}{\nolinkurl{https://doi.org/10.1002/asi.24002}}

[J4] \underline{Li, K.}, Rollins, J., \& Yan, E. (2018). Web of Science use in published research and review papers 1997–2017: a selective, dynamic, cross-domain, content-based analysis. \textit{Scientometrics}, 115(1), 1-20. \href{https://doi.org/10.1007/s11192-017-2622-5}{\nolinkurl{https://doi.org/10.1007/s11192-017-2622-5}} 

[J3] Zhao, M., Yan, E., \& \underline{Li, K.} (2018). Data set mentions and citations: A content analysis of full- text publications. \textit{Journal of the Association for Information Science and Technology}, 69(1): 32-46. \href{https://doi.org/10.1002/asi.23919}{\nolinkurl{https://doi.org/10.1002/asi.23919}}

[J2] \underline{Li, K.} \& Yan, E. (2018). Co-mention network of R packages: Scientific impact and clustering structure. \textit{Journal of Informetrics}, 12(1): 87-100. \href{https://doi.org/10.1016/j.joi.2017.12.001}{\nolinkurl{https://doi.org/10.1016/j.joi.2017.12.001}}

[J1] \underline{Li, K.}, Yan, E., \& Feng, Y. (2017). How is R cited in research outputs? Structure, impacts, and citation standard. \textit{Journal of Informetrics}, 11(4): 989-1002. \href{https://doi.org/10.1016/j.joi.2017.08.003}{\nolinkurl{https://doi.org/10.1016/j.joi.2017.08.003}}

\textbf{Refereed Full Papers in Conference Proceedings}

[C4] \underline{Li, K.}, \& Yan, E. (2019). Using a keyword extraction pipeline to understand concepts in future work sections of research papers. In \textit{17th International Conference on Scientometrics and Informetrics}.

[C3] Feng, Y., \underline{Li, K.}, \& Agosto, D.E. (2017). Healthy users’ personal health information management from activity trackers: The perspective of gym-goers. In \textit{Proceedings of the Annual Meeting of Association for Information Science and Technology} (54: pp. 71-81). \href{https://doi.org/10.1002/pra2.2017.14505401009}{\nolinkurl{https://doi.org/10.1002/pra2.2017.14505401009}}

[C2] \underline{Li, K.}, Greenberg, J., \& Lin, X. (2016). Software Citation, Reuse and Metadata Considerations: An Exploratory Study Examining LAMMPS. In \textit{Proceedings of the Annual Meeting of the Association for Information Science and Technology} (53: pp. 1-10). \href{https://doi.org/10.1002/pra2.2016.14505301072}{\nolinkurl{https://doi.org/10.1002/pra2.2016.14505301072}}

[C1] Qin, J., \& \underline{Li, K.} (2013). How portable are the metadata standards for scientific data? a proposal for a metadata infrastructure. In \textit{Proceedings of the International Conference on Dublin Core and Metadata Applications} (pp. 25–34). \href{https://dcpapers.dublincore.org/pubs/article/view/3670}{\nolinkurl{https://dcpapers.dublincore.org/pubs/article/view/3670}}

\textbf{Refereed Short Papers in Conference Proceedings}

[S6] \underline{Li, K.}, Chen, J., \& Ni, C. (2023). The patterns of publication languages used by STEM research in China. In \textit{19th International Conference on Scientometrics and Informetrics}.

[S5] \underline{Li, K.} \& Jiao, C. (2021). How are data paper abstracts constructed? Preliminary analysis of rhetorical moves in data paper abstracts from Scientific Data and Data in Brief. In \textit{18th International Conference on Scientometrics and Informetrics}.

[S4] Dagiene, E. \& \underline{Li, K.} (2021). ISBNs as identifiers for books in research evaluations. In \textit{18th International Conference on Scientometrics and Informetrics}.

[S3] Ma, R., \underline{Li, K.}, \& He, D. (2021). Understanding the Narrative Functions of Visualization in Digital Humanities Publications: A Case Study of the Journal of Cultural Analytics. In \textit{Proceedings of iConference 2021}.

[S2] Pascua, S., \underline{Li, K.}, \& Greenberg, J. (2019). Toward A Metadata Activity Matrix: Conceptualizing and Grounding the Research Life-cycle and Metadata Connections. In \textit{Proceedings of the International Conference on Dublin Core and Metadata Applications}.

[S1] Guerra, J., Wei, Q., \underline{Li, K.}, Ahumada, L., Winston, F., \& Desai, B. R. (2018). Scosy: A Biomedical Collaboration Recommendation System. Presented at the 40th Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC), Honolulu, HI, USA.

\textbf{Refereed Conference Posters}

[P9] \underline{Li, K.}, Zheng, X., & Ni, C. (2023). Gender disparities in the STEM research enterprise of China. 2nd International Conference of Science of Science & Innovation, Evanston, IL, USA.

[P8] Chen, PY, \underline{Li, K.} \& Jiao, C. (2022), A Preliminary Analysis of Geography of Collaboration in Data Papers by S\&T Capacity Index. \textit{Proceedings of the Association for Information Science and Technology}, 59: 642-644.

[P7] Ma, R.Q. \& \underline{Li, K.} (2020). Telling Multifaceted Stories with Humanities Data: Visualizing Book of Hours Manuscripts. Presented at iConference 2020 Annual Meeting. (Finalist for Best Poster Award).

[P6] \underline{Li, K.}, Chen, P.-Y., \& Fang, Z. (2019). Disciplinarity of Software Papers: A Preliminary Analysis. In \textit{Proceedings of the Annual Meeting of Association for Information Science and Technology}.

[P5] \underline{Li, K.}, \& Chen, P.-Y. (2019). A preliminary scientometric analysis of the Cross-Strait scientific collaboration. In \textit{17th International Conference on Scientometrics and Informetrics}.

[P4] He, J. \& \underline{Li, K.} (2019). How comprehensive is the PubMed Central Open Access full-text database?. Presented at iConference 2019 Annual Meeting, Washington, DC, USA. \href{http://hdl.handle.net/2142/103317}{http://hdl.handle.net/2142/103317}

[P3] \underline{Li, K.} \& Chen, PY. (2018). The narrative structure as a citation context in data papers: A preliminary analysis of Scientific Data. In \textit{Proceedings of the Annual Meeting of Association for Information Science and Technology}. \href{https://doi.org/10.1002/pra2.2018.14505501147}{\nolinkurl{https://doi.org/ 10.1002/pra2.2018.14505501147}}

[P2] \underline{Li, K.} \& Xu, S. (2017). Measuring the impact of R packages. In \textit{Proceedings of the Annual Meeting of Association for Information Science and Technology} (54: pp. 739-741). \href{https://doi.org/10.1002/pra2.2017.14505401138}{\nolinkurl{https://doi.org/10.1002/pra2.2017.14505401138}}

[P1] \underline{Li, K.} (2016). How much can data citation standards be used for scientific software? A crosswalk analysis of data citation standards for software citation needs. Presented in Research Data Alliance 8th Plenary Meeting, Denver, Colorado, September 14-17, 2016.

\textbf{Book Reviews}

[B1] \underline{Li, K.} (2019). A review of The Politics of Mass Digitization. \textit{Education for Information}, 35, 361-363. \href{https://doi.org/10.3233/EFI-199011}{\nolinkurl{https://doi.org/10.3233/EFI-199011}}

\textbf{Doctoral Colloquia (Lightly Peer-Reviewed)}

[D2] \underline{Li, K.} (2019). Quantitative examination of research methods and software in scientific publications. Selected to attend the Doctoral Colloquium at ASIS\&T 2019, Melbourne, Australia, October 19, 2019.

[D1] \underline{Li, K.} (2019). What is the discplinarity of software. Selected to attend the Doctoral Forum at 17th International Conference on Scientometrics and Informetrics, Rome, Italy, September 2, 2019.

\textbf{Non-Refereed Conference Presentations}

[T1] \underline{Li, K.} (2012). RDA in China. Presented at ALA Annual Conference 2012. June 24, 2012. Anaheim, California.

\section{TEACHING EXPERIENCE}

\textbf{Instructor}

School of Information Sciences, University of Tennessee, Knoxville
\begin{itemize}
\item \textbf{INSC 512: Information Organization \& Retrieval} (Spring '23, Fall '23)
\end{itemize}

School of Information Resource Management, Renmin University of China
\begin{itemize}
\item \textbf{Information Visualization in the Context of Digital Humanities} (Master level) (Fall '21, '22)
\item \textbf{Information Visualization} (Undergraduate level) (Spring '22)
\item \textbf{Knowledge Organization} (Master level) (Spring '22)
\end{itemize}

College of Computing \& Informatics, Drexel University

\begin{itemize}
\item \textbf{INFO 250: Information Visualization} (Online) (Summer '20)
\item \textbf{INFO 590: Foundations of Data and Information} (Online) (Winter '20)
\item \textbf{INFO 250: Information Visualization} (On-site) (Summer '19)
\end{itemize}

\section{HONORS \& AWARDS}


{\sl IAS Collaborative Award}  \hfill 2023-2024 \\
\textbf{Indiana University}
\begin{itemize}
\item Co-PI
\item Project: Empirical Exploration of the Visual Language in Digital Humanities
\item Awarded \$6,000
\end{itemize} 

{\sl LIS Education and Data Science for the National Digital Platform (LEADS-4-NDP) Fellowship}  \hfill 2019 \\
\textbf{Drexel University}
\begin{itemize}
\item Project: Automatic Identification of Publisher Entities to Support Discovery and Navigation (with OCLC)
\item Awarded \$5,000 plus travel support
\end{itemize} 

{\sl RDA/US Data Share Fellowship}  \hfill 2016 - 2017 \\
\textbf{Research Data Alliance}
\begin{itemize}
\item Project: Metadata Standards and Software Citation Practices
\item Awarded \$10,000 plus travel support
\end{itemize} 

{\sl Student Travel Award} \hfill 2019 \\
\textbf{The International Society for Informetrics and Scientometrics}

% Service and Membership
\section{SERVICE \& MEMBERSHIPS}

\textbf{Editorial Board}
\begin{itemize}
\item \textbf{Annual Review of Information Science and Technology (ARIST)}, 2022-2024
\end{itemize}

\textbf{Service}
\begin{itemize}
\item \textbf{President}, ASIS\&T SIG-MET, 2023-2024
\item \textbf{President-Elect}, ASIS\&T SIG-MET, 2022-2023
\item \textbf{Jury}, ASIS\&T Lois Lunin Award, 2022, 2023
\item \textbf{Mentor}, ASIS\&T Mentor Program, 2022-2023
\item \textbf{Webmaster}, ASIS\&T SIG-MET, 2021-2022
\item \textbf{Committee Member}, ISSI 2021 Paper of the Year Award Committee, 2021
\item \textbf{Secretary}, ASIS\&T SIG-MET, 2020-2021
\item \textbf{Award Coordinator}, ASIS\&T SIG-MET, 2019-2020
\end{itemize}

\textbf{Selected Peer Review Experience}:  
(My full peer review record can be retrieved from my ORCID page.)

\begin{itemize}
\item Journal of the Association for Information Science and Technology
\item Humanities and Social Sciences Communications
\item Scientific Reports
\item Quantitative Science Studies
\item Scientometrics
\item Journal of Informetrics
\item Journal of Information Science
\item PLoS ONE
\end{itemize}

\textbf{Membership}
\begin{itemize}
\item The Association for Information Science and Technology (ASIS\&T)
\end{itemize}

% Professional Experience
\section{PROFESSIONAL EXPERIENCE}

\textit{Cataloger} \hfill 2014 - 2015\\
\textbf{Ingram Content Group, Fort Wayne, Indiana}

\textit{Cataloging Librarian} \hfill 2007 - 2012\\
\textbf{Capital Library of China, Beijing, China}


%----------------------------------------------------------------------------------------

\end{resume}
\end{document}